Measurement of total hadronic differential cross sections in the LArIAT experiment

### 2018-04-27 Chapter-9/9-Uncertainty.tex
s

>>>>

\textbf{Systematics}
Discrepancies between the real TPC geometry and the simulated geometry can lead to a systematic in the $E_{loss}$ calculation. In particular, we found a difference in the depth of the un-instrumented argon upstream to the TPC front face, the MC geometry reporting $~\sim 3.3$ cm more un-instrumented argon than the TPC survey. For a pion MIP, this depth corresponds to 7.4 MeV which we account for as a double sided systematic in the determination of the pion kinetic energy.
